To Airbnb?: A Question of Returns

### 2018-05-21 _old/abb_Writeup_ARES.Rmd
isolating old code

<!-- \autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries. -->

<!-- ```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'} -->

<!--  load(paste0(fig.path, 'suburbMap.RData')) -->

<!--  loc.map <- loc.map + -->
<!--    theme(axis.title.y=element_blank(), -->
<!--          axis.text.y=element_blank(), -->
<!--          axis.ticks.y=element_blank(), -->
<!--          axis.title.x=element_blank(), -->
<!--          axis.text.x=element_blank(), -->
<!--          axis.ticks.x=element_blank()) -->

<!--  loc.map -->

<!-- ``` -->

@@

@@

>>>>

\autoref{locmap} shows the three large submarkets (Inner, Middle and Outer) and the individual suburbs boundaries.

```{r plot_suburbmap, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap='\\label{locmap}Melbourne Submarkets'}

 load(paste0(fig.path, 'suburbMap.RData'))

 loc.map <- loc.map +
   theme(axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank(),
         axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())
  ggsave(loc.map, filename=file.path(fig.path, 'loc_map.png'),
         bg='transparent',
         width=6, height=6)
 # loc.map

![Suburb Categories](c://dropbox/research/airBnb/figures/loc_map.png)

@@

    ggsave(str.map, filename=file.path(fig.path, 'str_map.png'),
         bg='transparent',
         width=6, height=6)
    ggsave(ltr.map, filename=file.path(fig.path, 'ltr_map.png'),
         bg='transparent',
         width=6, height=6)

@@

![Short Term Rental Locations](c://dropbox/research/airBnb/figures/str_map.png)

![Long Term Rental Locations](c://dropbox/research/airBnb/figures/ltr_map.png)
